Switch equivalence and weak prime domains for fusions

### 2023-12-15 fusione.tex
cose

\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
	If $\phi\colon G\to G'$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]

@@

@@

The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
\begin{lemma}
	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$. If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
	Then
	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
\end{lemma}

@@

\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
\begin{align*}
	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D},  \alpha, \omega \circ \beta^{-1}\circ \xi)\\
	(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}',  \alpha', \omega' \circ (\beta')^{-1}\circ \xi')
\end{align*}
In this case we have that $E=K$ and that $\pi(E)=\pi(E')$. From \Cref{rem:empty} we deduce that the diagram below commutes.
\[\xymatrix@C=35pt{\pi(E) \ar[r]^{\xi} \ar[d]_{\id{\pi(E)}}& E  \ar[d]_{\varphi_E}\ar[r]^-{\beta^{-1}} & \pi(E) \ar[d]_{\id{\pi(E)}} \ar[r]^{\omega}& H \ar[d]^{\phi_H}\\\pi(E') \ar[r]_{\xi'}& E' \ar[r]_-{(\beta')^{-1}} & \pi(E') \ar[r]_{\omega'} & H'}\]
The thesis now follows at once.
	\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
	\begin{align*}
		(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D}*\omega^{-1}\cdot \beta*\der{E}, \alpha, \xi)\\
		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}'*(\omega')^{-1}\cdot \beta'*\der{E'}, \alpha', \xi')
	\end{align*}
 To fix the notation, suppose that $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ are given by
	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^t \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^t\]
	where $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams. We can also notice that the rule applied by $\dder{D}_i$ must coincide with the one applpied in $\dder{D}'_i$ and that the same holds for $\dder{E}_i$ and $\dder{E}'_i$.
	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G_i & D_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E_{i+1}}\]

@@

To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ it is now enough to prove the commutativity of the diagrams
	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]

@@

	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro}\]
\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
\end{definition}

@@

\begin{remark}\label{rem:comp} Consistent permutations can be composed. Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
	\[\xymatrix@C=18pt{ & G \ar[rr]^{\iota_{G}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  H \ar[rr]^{\iota_H} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G' \ar[rr]^{\iota'_{G'}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi(H)\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & H' \ar[rr]^{\iota'_{H'}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}  \ar[rr]_{\hat{\iota}_{\hat{G}}}&& \lpro \hat{\der{D}}\rpro  && \hat{H} \ar[rr]_{\hat{\iota}_{\hat{H}}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
\end{remark}

@@

\begin{proposition}\label{prop:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
If $\sigma_1\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\sigma_2:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then 
\[\sigma_1+\sigma_2\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
	\sigma_1(n) & n < \lgh(\der{D}_1)\\
	\sigma_2(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
\end{cases}\]
 is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
\end{proposition}
\begin{proof}
	\[(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega'):=\begin{cases}
		(\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')	&\lgh(\der{D})=0 \\
		(\der{D}, \alpha, \omega \circ (\alpha')^{-1}\circ \omega')&\lgh(\der{D}')=0 \text{ and } \lgh(\der{D})\neq 0\\
		(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')	&\text{otherwise}
	\end{cases}\]

	Following \Cref{def:conc}, we will split the proof in three cases.
	\begin{itemize}
		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
		\[(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \quad (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
	Moreover, in this case $\sigma_1+\sigma_2=\sigma_2$. The thesis now follows at once noticing that 
	\begin{align*}\xi_{\sigma_2}\circ \iota_{G_{2,0}}\circ \alpha_2 \circ \omega_1^{-1}\circ \alpha_1 &=\iota'_{G'_{2,0}} \circ \alpha'_2 \circ \omega^{-1}_1 \circ \alpha_1\\&=\iota'_{G'_{2,0}} \circ \alpha'_2 \circ (\omega'_1)^{-1}\circ \xi_{\id{\emptyset}} \circ \alpha_1\\&=\iota'_{G'_{2,0}} \circ \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1
	\end{align*}

		\item 
		\item  \qedhere 
	\end{itemize}
\end{proof}

>>>>

\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
	If $\phi\colon G'\to G$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
	\[\xymatrix{L \ar[d]_{\phi^{-1} \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi^{-1} \circ f} D \ar[r]_{\psi \circ g}& H'}\]

@@

\begin{example}\label{rem:absequi}
	Let $\der{D}$ be a derivation with source $G$ and target $H$. Let also $\phi:G'\to G$ and $\psi:H\to H'$ be two isomorphisms. Then for every $X\in \Deltamin(\der{D})$ we can define 
	\[\varphi_X:=\begin{cases}
		\phi^{-1} & X=G\\
		\psi & X=H\\
		\id{X} & \text{otherwise}
	\end{cases}\]

It is immediate to see that the family $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}*\psi$.	
\end{example}

@@

The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
\begin{lemma}\label{lem:conc}
	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$. If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
	Then
	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
\end{lemma}

@@

\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
\begin{align*}
	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D},  \alpha, \omega \circ \beta^{-1}\circ \xi)\\
	(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}',  \alpha', \omega' \circ (\beta')^{-1}\circ \xi')
\end{align*}
In this case we have that $E=K$ and that $\pi(E)=\pi(E')$. From \Cref{rem:empty} we deduce that the diagram below commutes.
\[\xymatrix@C=35pt{\pi(E) \ar[r]^{\xi} \ar[d]_{\id{\pi(E)}}& E  \ar[d]_{\varphi_E}\ar[r]^-{\beta^{-1}} & \pi(E) \ar[d]_{\id{\pi(E)}} \ar[r]^{\omega}& H \ar[d]^{\phi_H}\\\pi(E') \ar[r]_{\xi'}& E' \ar[r]_-{(\beta')^{-1}} & \pi(E') \ar[r]_{\omega'} & H'}\]
The thesis now follows at once.
	\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
	\begin{align*}
		(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D}*\omega^{-1}\cdot \beta*\der{E}, \alpha, \xi)\\
		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}'*(\omega')^{-1}\cdot \beta'*\der{E'}, \alpha', \xi')
	\end{align*}
 To fix the notation, suppose that $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ are given by
	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^t \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^t\]
	Moreover, noticing that the rule applied by $\dder{D}_i$ and the one applied in $\mathcal{E}_i$  must coincide with, respectively, the one applied in $\dder{D}'_i$ and the one applied $\dder{E}'_i$. We will also assume that $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams. 
	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G'_i & D'_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G'_{i+1} & E'_i & F'_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E'_{i+1}}\]

@@

To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ is an abstraction equivalence, it is now enough to prove the commutativity of the diagrams
	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]

@@

	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar@{>->}[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar@{>->}[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
\end{definition}

@@

\begin{remark}\label{rem:comp} Consistent permutations can be composed. Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ all of length $n$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
	\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{n} \ar@{>->}[rr]^{\iota_{ G_{n}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi({ G_{n}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{n}} \ar@{>->}[rr]^{\iota'_{{ G'_{n}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_n \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_n}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
\end{remark}

@@
